### 2020-04-25 README.Rmd
Add travis and testthat

---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/tidySEM)](https://cran.r-project.org/package=tidySEM)
[![](https://cranlogs.r-pkg.org/badges/tidySEM)](https://cran.r-project.org/package=tidySEM)-->
<!--[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build
status](https://travis-ci.org/cjvanlissa/tidySEM.svg?branch=master)](https://travis-ci.org/cjvanlissa/tidySEM)
[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/tidySEM/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/tidySEM?branch=master)
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
# WORCS

@@

```{r echo = FALSE, results='asis'}
descripts <- c(
  "_pkgdown.yml" = "YAML for package website (do not edit)",
  "DESCRIPTION" = "R-package DESCRIPTION (do not edit)",
  "LICENSE.md" = "Project license (do not edit)",
  "NAMESPACE" = "R-package namespace (machine-written)",
  "README.md" = "Read this file to get started!  (do not edit)",
  "README.Rmd" = "R-markdown source for readme.md (human editable)",
  "worcs.Rproj" = "Rstudio project file (do not edit)",
  "docs/" = "Package website (machine-written)",
  "inst/" = "Rstudio project template files  (human editable)",
  "man/" = "R-package documentation (do not edit)",
  "paper/" = "WORCS paper source files (human editable)",
  "R/" = "R-package source code (human editable)",
  "vignettes/" = "R-package vignettes (human editable)"
)
prioritize <- c(
  "README.md",
  "LICENSE.md",
  grep("^(?:(?!/).)*$", names(descripts), value = TRUE, perl = TRUE)
)
prioritize <- unique(prioritize)
f <- list.files(recursive = T)
struc <- f[!grepl("/", f)]
dirs <- f[grepl("/", f)]
dirs <- unique(gsub("/.*$", "/", dirs))

struc <- c(struc, dirs)

struc <- data.frame(file = struc)
struc$desc <- ""
struc$desc[match(struc$file, names(descripts))] <- descripts[match(struc$file, names(descripts))]

prioritize <- match(prioritize, struc$file)
ord <- c(prioritize, c(1:nrow(struc))[-prioritize])
struc <- struc[ord, ]

pd <- paste0("%", -1*(max(nchar(levels(struc$file)))+2), "s")
out <- c("```", ".", apply(struc, 1, function(thisrow){
  paste0("├── ", sprintf(pd, thisrow[1]), "<- ", thisrow[2])
}), "```")
cat(out, sep = "\r\n")
```

@@

``` r
install.packages("devtools")
devtools::install_github("cjvanlissa/tidySEM")
```

@@

  - File a GitHub issue [here](https://github.com/cjvanlissa/tidySEM)
  - Make a pull request
    [here](https://github.com/cjvanlissa/tidySEM/pulls)

>>>>

---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
<!--[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)-->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
# WORCS

@@

```{r echo = FALSE, results = "asis"}
descripts <- data.frame(matrix(c(
  "_pkgdown.yml", "YAML for package website", "do not edit",
  "DESCRIPTION", "R-package DESCRIPTION", "do not edit",
  "LICENSE.md", "Project license", "do not edit",
  "NAMESPACE", "R-package namespace", "machine-written",
  "README.md", "Read this file to get started! ", "do not edit",
  "README.Rmd", "R-markdown source for readme.md", "human editable",
  "worcs.Rproj", "Rstudio project file", "do not edit",
  "docs/", "Package website", "machine-written",
  "inst/", "Rstudio project template files ", "human editable",
  "man/", "R-package documentation", "do not edit",
  "paper/", "WORCS paper source files", "human editable",
  "R/", "R-package source code", "human editable",
  "vignettes/", "R-package vignettes", "human editable"
), ncol = 3, byrow = TRUE))
names(descripts) <- c("File", "Description", "Usage")
knitr::kable(descripts)
```

@@

``` r
install.packages("devtools")
devtools::install_github("crsh/papaja", dependencies = TRUE)
devtools::install_github("cjvanlissa/worcs", dependencies = TRUE)
tinytex::install_tinytex()
worcs::git_credentials("your_name", "your_email")
```

@@

  - File a GitHub issue [here](https://github.com/cjvanlissa/worcs)
  - Make a pull request
    [here](https://github.com/cjvanlissa/worcs/pulls)
